\thesistitle

### 2019-08-25 sections/discussion.tex
Discussion

\section{Automated Refactoring}
In this section, we discuss our implementation decisions to refactor source code using CloneRefactor and measure its impact.

@@

\subsection{Complex control flow}
Break, continue and return statements can obstruct the possibility of performing method extraction. However, with some extra transformations, method extraction will still be possible in such cases. Figure \ref{fig:complexcontrolflowrefactoring} shows such a transformation. We can wrap the newly extracted method in a conditional to indicate whether the ``control flow modifying statement'' should be executed. In other cases, other methods might apply to refactor such clones.

@@

\subsection{Clone Types}
In this section, we discuss the differences between clone types 1-3 and 1R-3R. We see that the difference between T1R and T1 in terms of found clones is small (11\% more nodes found as cloned for T1). This implies that most often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (35\% more nodes found as cloned). Upon manual inspection, we found that the main reason for this is that T2R does not allow any variability in types, whereas T2 allows any variability in types.

Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Type 1R-3R take on average approximately 6 times longer to detect than type 1-3. The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable-, and method-references.

In Figure~\ref{fig:t2rgraph} we show the increase of cloned nodes for a higher variability between clone instances. This graph is logarithmic: as the variability increases, the increase in nodes decreases. This implies that semantical equality increases the chances that tokens are equal.

In Figure~\ref{fig:t3rgraph} we show the increase of cloned nodes for higher type 3R gap sizes. The line denoting the number of clone classes seems a bit exponential whereas the line denoting cloned nodes is mostly linear. This makes sense regarding the nature of the threshold. Type 3R clones are formed by merging two gapped clone classes into a type 3R clone class. As we get into higher gap size percentages, fewer clone classes merge. However, at these higher gap size percentages, the gaps contain more nodes. Because of this, the increase of the number of cloned nodes is linear.

@@

\subsubsection{Token Volume}
In Fig.~\ref{fig:maintainabilityscore} we see an increase in the \textbf{maintainability score} for refactoring larger clone classes. The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, lies at a token volume of 63 tokens. There are fewer large clones than small clones (exponential decrease), resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.

When looking at the relation between maintainability and the \textbf{volume} metric, we see that the volume increases if the average clone volume is less than 60 tokens, but decreases above 60 tokens. When token volume increases, the \textbf{number of parameters} of the extracted method rises very slowly. Overall, on average, extracted methods have only one parameter. When the token volume of clones becomes larger than 160 tokens, we also see that there are more outliers in terms of the number of parameters. For the \textbf{complexity} we see that most clones do not have any complexity, because for most refactorings the complexity increases by one. This complexity is the added complexity of the extracted method and implies that the removed clones did not have any complexity. There is also no clear trend regarding the complexity metric against the token volume.

@@

The maintainability scores displayed in Table~\ref{tab:relationref} show that the most favorable clones to refactor are clones with a superclass relation. The most unfavorable is to refactor unrelated clones. The main reason for this difference in maintainability is that on average unrelated clones have a higher volume.

The differences in maintainability of relation are, compared to the differences in maintainability of different token volumes, very small. Common hierarchy (which has the highest score) has a maintainability score of 0.23 whereas unrelated clones (which has the lowest score) have a maintainability score of -0.15. This is a very small difference, which implies that according to our data relations have a minor impact on the maintainability of clones.

>>>>

\section{Automated Refactoring}
In this section, we discuss our implementation decisions regarding the automated refactoring of source code using CloneRefactor.

@@

\subsection{Complex control flow}
\texttt{break}, \texttt{continue} and \texttt{return} statements can obstruct the possibility of performing method extraction. However, with some extra transformations, method extraction will still be possible in such cases. Figure \ref{fig:complexcontrolflowrefactoring} shows such a transformation. We can wrap the newly extracted method in a conditional to indicate whether the ``control flow modifying statement'' should be executed. In other cases, other methods might apply to refactor such clones.

@@

\subsection{Clone Types}
In this section, we discuss the differences between clone types 1-3 and 1R-3R.

\subsubsection{Cloned Nodes}
We see that the difference between T1R and T1 in terms of found clones is small (11\% more nodes found as cloned for T1). This implies that most often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (35\% more nodes found as cloned). Upon manual inspection, we found that the main reason for this is that T2R does not allow any variability in types, whereas T2 allows any variability in types.

\subsubsection{Performance}
Regarding performance (Figure~\ref{fig:performance}), there is a notable difference between the refactoring-oriented clone types and the literature clone types. Type 1R-3R take on average approximately 6 times longer to detect than type 1-3. The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable-, and method-references.

\subsubsection{Type 2R Variability}
In Figure~\ref{fig:t2rgraph} we show the increase of cloned nodes for a higher variability between clone instances. This graph is logarithmic: as the variability increases, the increase in nodes decreases. This implies that semantical equality increases the chances that tokens are equal.

\subsubsection{Type 3R Gap Size}
In Figure~\ref{fig:t3rgraph} we show the increase of cloned nodes for higher type 3R gap sizes. The line denoting the number of clone classes seems a bit exponential whereas the line denoting cloned nodes is mostly linear. This makes sense regarding the nature of the threshold. Type 3R clones are formed by merging two gapped clone classes into a type 3R clone class. As we get into higher gap size percentages, fewer clone classes merge. However, at these higher gap size percentages, the gaps contain more nodes. Because of this, the increase of the number of cloned nodes is more linear.

@@

\subsubsection{Token Volume}
In Fig.~\ref{fig:maintainabilityscore} we see an increase in the \textbf{maintainability score} for refactoring larger clone classes. The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, lies at a token volume of 63 tokens. There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.

When looking at the relation between maintainability and the \textbf{volume} metric, we see that on average the delta volume increases if the average clone volume is less than 60 tokens, but decreases above 60 tokens. When token volume increases, the \textbf{number of parameters} of the extracted method rises very slowly. Overall, on average, most extracted methods have only one parameter. When the token volume of clones becomes larger than 160 tokens, we also see that there are more outliers in terms of the number of parameters. For the \textbf{complexity} we see that most clones do not have any complexity, because for most refactorings the complexity increases by one. This complexity is the added complexity of the extracted method and implies that the removed clones did not have any complexity. There is also no clear trend regarding the complexity metric against the token volume.

@@

The maintainability scores displayed in Table~\ref{tab:relationref} show that the most favorable clones to refactor are clones with a \textit{superclass} relation. The most unfavorable is to refactor \textit{unrelated} clones. The main reason for this difference in maintainability is that on average unrelated clones have a higher volume.

The differences in maintainability of relation are, compared to the differences in maintainability of different token volumes, very small. \textit{Common hierarchy} (which has the highest score) has a maintainability score of 0.23 whereas \textit{unrelated} clones (which has the lowest score) have a maintainability score of -0.15. This is a very small difference, which implies that according to our data relations have a minor impact on the maintainability of clones.
